Model Checking Differentially Private Properties

### 2018-06-12 specifications.tex
minor
minor change

For the $\frac{1}{2}$-geometric mechanism (Section~\ref{subsec:geometric}),
define the formula
$\psi = \dpriv{\ln 2}{0} (\X out_0) \wedge \dpriv{\ln 2}{0} (\X out_1) \wedge
\cdots \wedge \dpriv{\ln 2}{0} (\X out_5)$. If the state $s_k$ satisfies
$\psi$ for $k = 0, \ldots, 5$, then the $\frac{1}{2}$-geometric mechanism is
$(\ln 2, 0)$-differentially private. For the subsampling majority
mechanism (Section~\ref{subsection:subsampling}), consider the formula
$\psi = \dpriv{\epsilon, \delta} (\F 0) \wedge \dpriv{\epsilon,
  \delta} (\F 1)$. If a state satisfies $\psi$, its probability of
outputting is $(\epsilon, \delta)$-close to those of its
neighbor for every outcomes. The subsampling majority
mechanism is $(\epsilon, \delta)$-differentially private.

>>>>

For the $\frac{1}{2}$-geometric mechanism (Section~\ref{subsec:geometric}),
define the formula
$\psi = \dpriv{\ln 2}{0} (\X out_0) \wedge \dpriv{\ln 2}{0} (\X out_1) \wedge
\cdots \wedge \dpriv{\ln 2}{0} (\X out_5)$. If the state $s_k$ satisfies
$\psi$ for $k = 0, \ldots, 5$, then the $\frac{1}{2}$-geometric mechanism is
$(\ln 2, 0)$-differentially private. For the subsampling majority
mechanism (Section~\ref{subsection:subsampling}), consider the formula
$\psi = \dpriv{\epsilon}{\delta} (\F 0) \wedge \dpriv{\epsilon}
  {\delta} (\F 1)$. If a state satisfies $\psi$, its probability of
outputting is $(\epsilon, \delta)$-close to those of its
neighbor for every outcomes. The subsampling majority
mechanism is $(\epsilon, \delta)$-differentially private.
